Palomar 5 Gaps

### 2024-10-28 paper/main.tex
fixed up comment on NGC2808 impact on number of gaps per simulation

    Overall, across 50 simulations, we observe 73 gaps. The distribution of simulations with a given number of gaps is as follows: \begin{tabular}{|l|c|c|c|c|c|}
      \hline
      Number of Gaps & 0 & 1 & 2 & 3 & 4 \\
      \hline
      Number of Sims. & 4 & 25 & 16 & 4 & 1 \\
      \hline
    \end{tabular} Excluding NGC~2808, we are left with 29 gaps, leading to an expected range of 0.6-1.5 gaps per simulation.

>>>>

    Overall, across 50 simulations, we observe 73 gaps. The distribution of simulations with a given number of gaps is as follows: \begin{tabular}{|l|c|c|c|c|c|}
      \hline
      Number of Gaps & 0 & 1 & 2 & 3 & 4 \\
      \hline
      Number of Sims. & 4 & 25 & 16 & 4 & 1 \\
      \hline
    \end{tabular} If we consider NGC 2808 to be an outlier and exclude it from the experiment, we observe an average of 0.6 gaps per simulation. Including all observed gaps results in an average of 1.5 gaps per simulation.
